Testing and Isolation Efficacy; Insights from a Simple Epidemic Model

### 2020-11-23 SIR_manuscript.tex
some updates

@@

Some of the underlying assumptions of the model \eqref{model} are as follows: (i) all groups are being exposed to all others, (ii) there is a single force of infection, $\Lambda$, that is, where a susceptible individual moves to does not depend on who infected it, (iii) a perfectly specific test, $p_S=0$, for simplicity in analysis, (iv)  $\eta_t \leq \eta_w$, i.e., the individuals awaiting test results have a higher transmission probability than the reported individuals. 
- [Q] why not birth and death are included?

The Disease-Free Equilibrium, DFE hereafter, for the SIR model \ref{model} is given by solving the coupled system including $S_u+S_n=N_0$ and $F_S S_u-\omega S_n=0$. The DFE is

@@

 [Fady? \fady{I didn't do any simulations though}] 
 Something needs to be said here about simulation part which was done by using R, using the expression on $\Rnum$ and not the approximation, which give the panel plot in Figure \ref{pan}.
The analytical calculation of the next generation matrix, $G$, and the derivation of $\Rnum$ was carried out in Maple (ref) by using simple linear Algebra package. The numerical simulation of $\Rnum$ in the specified parameter space and plotting the contours of $\Rnum$ was carried out in R by using ggplot (ref?). It is notable that in the simulation part, the explicit expression of $\Rnum$ was used and not the approximation \eqref{eq:R0appr}. This simulation reflects the behavior of $\Rnum$ with respect to the selected parameters for two different testing strategies: (i) random testing, represented by all testing weights to be the same, $W_S=W_I=W_R$, and (ii) non-random testing, when testing weight are not equal. For simmulation purposes we chose $W_S=W_I=W_R=1$ for random testing, and $W_S=0.3$ and $W_I=W_R=1$ for non-random testing strategy. Note that the critical contour of $\Rnum=1$ is plotted in solid line in Figure \ref{pan}.

>>>>

\usepackage{xspace}
\newcommand{\Rlogo}{\protect\includegraphics[height=2ex,keepaspectratio]
{pix/Rlogo.pdf}\xspace}

@@

The classical SIR model is based on the following implicite assumptions (see a ref for details); well-mixed population, homogeneity of the population, exponentially distributed duration of infection and large population size (may be refer the reader to \cite{keeling2011modeling}). In addition to these standard assumptions, our model \eqref{model} assumes: (i) there is a single force of infection, $\Lambda$, that is, where a susceptible individual moves to does not depend on who infected it, (ii) a perfectly specific test, $p_S=0$, for simplicity in analysis, (iii)  $\eta_t \leq \eta_w$, i.e., the individuals awaiting test results have a higher transmission probability than the reported individuals. - [Q] why not birth and death are included? say it or not?

The Disease-Free Equilibrium (Ali, not sure if this is the right term?), DFE hereafter, for the SIR model \ref{model} is given by solving the coupled system including $S_u+S_n=N_0$ and $F_S S_u-\omega S_n=0$. The DFE is

@@

  [to be completed! Something needs to be said here about simulation part]. The analytical calculation of the next generation matrix, $G$, and the derivation of $\Rnum$ was carried out in Maple (ref) by using simple linear Algebra package. 
  We used \Rlogo for the simulation part which included using the explicite expression of $\Rnum$ \ref{R0} as a function of the underlying parameters, specifying the parameters a realistic range, calculating the corresponding $\Rnum$ and plotting the contours of $\Rnum$ by using ggplot package in \Rlogo. The related result is presented in Figure \ref{pan}, where  panel \eqref{p.a} represents the random testing, and panel \eqref{p.b} is representing non-random testing. The parameter values or ranges are as follows (I like using a table here, with the param, their units and values). It is notable that in the simulation part, the explicit expression of $\Rnum$ was used and not the approximation \eqref{eq:R0appr}. This simulation reflects the behavior of $\Rnum$ with respect to the selected parameters for two different testing strategies: (i) random testing, represented by all testing weights to be the same, $W_S=W_I=W_R$, and (ii) non-random testing, when testing weight are not equal. For simmulation purposes we chose $W_S=W_I=W_R=1$ for random testing, and $W_S=0.3$ and $W_I=W_R=1$ for non-random testing strategy. Note that the critical contour of $\Rnum=1$ is plotted in solid line in Figure \ref{pan}.
